\label{fig:3}
\textbf{Sleep is increased in \emph{DmCa\textsubscript{v}3} mutants}
\\
\textbf{(a)} Schematic representation of \emph{DmCa\textsubscript{v}3\textsuperscript{Gal4}} and \emph{DmCa\textsubscript{v}3\textsuperscript{Rescue}}. 
Red boxes indicate coding exons.
Genomic region within the arrows indicate deleted region.
SA, splicing acceptor. pA, polyA sequence.  
\textbf{(b)} Western blot analysis of DmCa\textsubscript{v}3 protein levels in \emph{DmCa\textsubscript{v}3\textsuperscript{Gal4}} and \emph{DmCa\textsubscript{v}3\textsuperscript{Rescue}} .
DmCa\textsubscript{v}3 protein is undetectable in \emph{DmCa\textsubscript{v}3\textsuperscript{Gal4}} while \emph{DmCa\textsubscript{v}3\textsuperscript{Rescue}}  shows a similar level as the \emph{w\textsuperscript{1118}} control.
$\beta$-actin was used for internal control.
\textbf{(c)} Sleep profiles of \emph{w\textsuperscript{1118}} (black, n=89), \emph{DmCa\textsubscript{v}3\textsuperscript{Gal4}} (red, n=92) and \emph{DmCa\textsubscript{v}3\textsuperscript{Rescue}}  (gray, n=61) over two days of 12h:12h light-dark cycle (LD) and two days of continuous dark condition (DD).
Sleep in 30 minute intervals was plotted.
Data are represented as mean $\pm$ SEM.
White, black and gray bar denote light phase, dark phase and subjective light phase, respectively.
ZT, zeitgeber time.
CT, circadian time.
\textbf{(d)} Averaged daily sleep amount in LD and DD.
\textbf{(e)} Waking activity in LD and DD.
Waking activity is total activity counts divided by waking minutes.
\textbf{(f)} The number of sleep bouts in LD and DD.
\textbf{(g)} Average length of a sleep bout in LD and DD.
In box-and-whisker plots, midline, upper and lower boundaries of each box represent median, 75\textsuperscript{th} and 25\textsuperscript{th} percentiles, respectively.
Upper and lower whiskers extend from hinge to the highest and lowest value within 1.5 $\times$ interquartile range of the upper and lower quartiles, respectively.
For statistical analysis, Welch's ANOVA followed by Games-Howell multiple comparison test was performed.
*p$<$0.05, **p$<$0.01, ***p$<$0.001.
  
  
  
  
  
  
  
  
  