\subsection*{Electrophysiological recordings and data analysis}

Barium (or Ca\textsubscript{v}3) currents through T-type channels expressed in oocytes were measured at room temperature 4 to 5 days after cRNA injection using a two-electrode voltage-clamp amplifier (OC-725C, Warner Instruments, Hamden, CT, USA).
Microelectrodes were pulled from the capillaries (Warner Instruments, Hamden, CT, USA) using a pipette puller and filled with 3 M KCl and the electrode resistance was 0.5-1.1 M$\Omega$.
The 10 mM Ba\textsuperscript{2+} (or Ca\textsubscript{v}3) recording solution contained (in mM): 10 Ba(OH)2 (or Ca(OH)2), 90 NaOH, 1 KOH, 5 HEPES (pH 7.4 adjusted with methanesulfonic acid).
To get rid of contamination of Ca\textsubscript{v}3-activated chloride currents, we injected 50 nl of 50 mM BAPTA into oocytes 30-60 min before recordings, especially for recording Ca\textsubscript{v}3 currents from oocytes.
The currents were usually sampled at 5 kHz and low pass filtered at 1 kHz using the pClamp system (Digidata 1320A and pClamp 8; Axon instruments, Foster City, CA, USA).
Data are presented as mean $\pm$ s.e.m.
The levels of significant difference(s) between groups were tested using Student's unpaired t-test: $p\le$0.05, $p\le$0.01, and $p\le$0.001 as the level of significance.
Activation and inactivation time constants of T-type channel currents elicited by step pulses were estimated by fitting individual current traces with a double exponential function: A1(1-exp(-t/$\tau$1)) + A2(1-exp(-t/$\tau$2)) where A1 and A2 are the coefficients for the activation and inactivation exponentials, t is time, and $\tau$1 and $\tau$2 are the activation and inactivation time constants, respectively.
The smooth curves for channel activation and steady-state inactivation were from fitting data with a Boltzmann equation: , where V50 is the potential for half-maximal activation and Sact is the slope conductance.
Dose-response curves for Ni\textsuperscript{2+} inhibition of T-type channel currents were derived by fitting the data using a Hill equation: B = 1/{1 + IC\textsubscript{50}/[Cd2+]n}, where B is the normalized block, IC\textsubscript{50} is the concentration of Ni\textsuperscript{2+} giving half maximal blockade, and n is the Hill coefficient.