\subsection*{DmCa\textsubscript{v}3 is broadly expressed in the adult brain}

To determine the expression pattern of DmCa\textsubscript{v}3 in the adult brain, we first generated a \emph{white\textsuperscript{+}} DmCa\textsubscript{v}3\textsuperscript{Founder} allele in which a $\phi$C31 attP landing site and a floxed \emph{mini-white} marker replaces the first coding exon of DmCa\textsubscript{v}3 via homologous recombination\cite{Huang:2009ei}.
We then removed the \emph{mini-white} marker via Cre-mediated recombination to produce a \emph{white\textsuperscript{-}} DmCa\textsubscript{v}3\textsuperscript{Founder} allele.
Finally, using $\phi$C31-mediated integration, we generated a GFP-tagged DmCa\textsubscript{v}3 knock-in allele, GFP::DmCa\textsubscript{v}3, by inserting the coding sequence for GFP in-frame immediately after the transcriptional start site of the first DmCa\textsubscript{v}3 exon (Fig. \ref{fig:S1}).
In GFP::DmCa\textsubscript{v}3 flies, GFP signal appears broadly across the brain, with the antennal lobes, mushroom body calyces, and the optic lobes all showing strong staining (Fig. \ref{fig:2}).
\todo[inline]{More figure panel references here?}%
The strongest expression, though, is in the central complex, which comprises the ellipsoid body, fan-shaped body, noduli, and protocerebral bridge (Fig. ).
GFP::DmCa\textsubscript{v}3 channels are also expressed broadly in less structured neuropils including subesophageal zone (SEZ), superior neuropil (SNP), inferior neuropil (INP), ventrolateral neuropil (VLNP) and ventromedial neuropil (VMNP).
\todo[inline]{All of these will be labeled in the figure?}% 

We next visualized the projections of DmCa\textsubscript{v}3-expressing neurons using another knock-in allele, DmCa\textsubscript{v}3\textsuperscript{Gal4}.
In DmCa\textsubscript{v}3\textsuperscript{Gal4}, the Gal4 coding sequence replaces the first coding exon of DmCa\textsubscript{v}3 and its flanking introns to drive GAL4 expression under the control of the endogenous DmCa\textsubscript{v}3 promoter (Fig. \ref{fig:S1}).
We visualized the projections of DmCa\textsubscript{v}3-positive neurons by using DmCa\textsubscript{v}3\textsuperscript{Gal4} to drive a membrane-tethered mCherry marker.
The strong co-localization of the mCherry signal in these flies with the GFP::DmCa\textsubscript{v}3 signal suggests both likely reflect the endogenous DmCa\textsubscript{v}3 expression pattern (Fig. \ref{fig:S2}).
\todo[inline]{Really? How does this mean it is the endogenous pattern? Did the GFP::DmCa\textsubscript{v}3 flies have a sleep phenotype? If you haven't done it, we should. Otherwise, how do we know the GFP tagged protein is functional?}%