\subsection*{Sleep and locomotor behavior analysis}

Fly sleep and locomotor behavior was measured with the \emph{Drosophila} Activity Monitoring system (Trikinetics).
For sleep analysis, 3-4 day-old female flies were placed individually into 65 mm X 5 mm glass tubes with one end filled with 2\% agar / 5\% sucrose food and the other end plugged with cotton.
We defined periods of activity as periods with a beam break frequency higher than 1 per minute and periods of sleep as periods during which no beam break occurred for at least 5 consecutive minutes\cite{Shaw:2000ui}.
After one day of habituation in an incubator (25$\,^{\circ}\mathrm{C}$, 60\% humidity), we used the ``Counting Macro'' software\cite{pfeiffenberger:2010ab} to measure sleep over the course of 4 days---2 days of 12 hr:12 hr light-dark conditions and 2 days of continuous darkness.
For experiments using the GeneSwitch technique, flies were maintained on normal food containing 500 $\mu$M RU486 (M8046, Sigma-Aldrich) dissolved in ethanol (1\%) for two days prior to the experiment.
Control flies were maintained on normal food containing only ethanol (1\%).
For the GeneSwitch experiments, flies were placed in 2\% agar / 5\% sucrose food with or without 500 $\mu$M RU486.
For sleep deprivation, activity monitors with 3-5 day-old female flies were placed in a Sleep Nullifying Apparatus (SNAP)\cite{shaw:2002aa} designed to rotate and give a swift mechanical stimulus twice per minute.
After three days under 12 hr:12 hr light-dark conditions, flies were sleep-deprived for 24 hr and allowed to recover 12 hr.
The percentage of lost sleep recovered (\% $\Delta$Sleep) was calculated by subtracting the baseline sleep (i.e., sleep during the light phase immediately before the deprivation day) from the amount of sleep during the recovery period and then dividing by sleep lost.
We confirmed that each genotype lost ~90\% of their baseline sleep during the deprivation period and we included only flies with $\geq$ 70\% sleep lost in the following calculations.
For the circadian locomotor analyses, we measured the activity of 1-3 day-old male flies in 30 minute bins and analyzed the data using ClockLab (Actimetrics) and the Counting Macro\cite{pfeiffenberger:2010aa}.
Significance level for the $\chi$\textsuperscript{2} periodogram was set to $\alpha$ = 0.05.
Flies with a power of significance (P-S) $\geq$10 were considered rhythmic.

  